Semantic High-definition Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-11-02 cvpr2018.tex
11th

%%%%%%%%% ABSTRACT
\begin{abstract}
This paper presents a novel and effective method to deal with the challenging task of generating synthetic photographic image conditioned on semantic image descriptions. We show a fully end-to-end trainable network that can generate high resolution images (e.g. $512^2$).
Our method leverages the deep representations of convolutional layers and introduces hierarchical-nested adversarial training to regularize the representations and capture the complex image statistics. We present a new network architecture, which is intuitive as well as extensile, to push generated images to high resolutions. \textcolor{red}{We present a functional generative adversarial networks (GANs) training strategy} to encourage more effective multimodal (i.e. image and text) information utilization in order to enhance multi-purpose adversary between real and fake distribution. 
With extensive experimental validation on three major datasets, our method significantly improves previous state of the arts.

@@

%%%%%%%%% BODY TEXT
\section{Introduction}
Generating photographic image conditional on arbitrary semantic description is an important problem in generative model research \cite{reed2016generative}. However, insufficient methods have been successfully developed to address this task due to its particular challenges. Text-to-image synthesis can be viewed as an special variation of conventional generative models, which aim to translate a low-dimensional embedding  to a much more complex RGB image space.  Differently, the embedding space of the former is induced by semantic descriptions. Therefore, this task requires the generated images to be \textit{semantically consistent}, i.e., the generated images not only preserve sketch concepts of descriptions generally but also preserve fine-grained descriptive details in image pixels.

Generative adversarial networks (GANs) have become the main solution to this task. 
Reed \etal \cite{reed2016generative} is th first to address this task through a GAN based framework. But this method only handles image up to $64{\times}64$ resolution and usually can barely generate vivid object details.
Based on this method, Zhang \etal \cite{han2017stackgan} present a successful approach (StackGAN) by stacking another GAN to generate high-quality $256{\times}256$ images given low resolution $64{\times}64$ synthetic images. This method needs two-stage training to achieve the goal. Later on, Dong \etal \cite{dong2017semantic} 
bypasses the difficult of translate vector embedding to RGB images and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-rendering an arbitrary-style training ($128{\times}128$) image conditioned on a targeting semantic description. Unfortunately, its high resolution synthesis ability is still unclear. 
At present, how to train from the low-dimensional text space to synthesize high resolution and diverse images in an end-to-end manner is still an open and attractive question.

We outline several empirical reasons for this challenges using GANs to deal with text-to-image synthesis. The first comes from a fundamental difficulty of balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}. How to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients. The second is that huge pixel space in high resolution images \cite{han2017stackgan}. 
An effective regularization to regularize generators is critical to help capture the complex image statistics \cite{huang2016stacked} as well as preserve semantic consistency. 
%The first reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. 
% Keeping semantic consistency as well as diversity
%The first reason comes from the fundamental difficulty of balancing the stability between generators and discriminators. There are a rich number of literature trying to stabilize GAN training \cite{salimans2016improved} and regularize networks \cite{huang2016stacked}. 
%But especially for text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important and needs careful consideration. The second reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators to generate effective gradients, as well as generators to prevent gradient vanishing. 
With careful consideration of these outlined problems, in this paper, we propose a novel fully end-to-end method that can directly model high resolution image statistics and generate semantic consistent and photographic image up to $512^2$ resolution. The contributions are described follows.

Our generator is a simple Vanilla GAN, without needing any inside text conditioning \cite{han2017stackgan} or image label supervision \cite{dash2017tac}. To tackle the problem of the big leap from the text space to the high resolution image space, our insight is to leverage hierarchical representations with additional implicit constraints to reduce training instability. 
We introduce ``accompanying'' hierarchically-nested adversarial objective at intermediate layers to generate multi-scale images.  
And we present an generator network structure design than can uses gradients from multi-scale nested discriminators more effectively.

To better make use of image and text information in GAN training, 
\textcolor{red}{we enforce discriminators at different resolutions can simultaneously differentiate real and fake image-text pairs, images, and patches.}
This multi-purpose conditional adversary is mutually beneficial to encourage each only focuses on respect duties. 
%It is a regularization to limit the discriminators to use unexpected information to make decision. 
We validate our proposed method on three datasets, i.e. CUB birds \cite{welinder2010caltech}, Oxford-102 flowers \cite{Nilsback08}, and large-scale COCO datasets \cite{lin2014microsoft}. Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts. All source code will be released.

\section{Related Work}
We discussed related methods as well as clarify the novelty of our method.

@@

Text-to-image synthesis not only requires diverse and high-quality generation but also requires precise semantically consistent mapping in the image space.  Reed \etal \cite{reed2016generative} introduce a method that can generate $64{\times}64$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}. This method presents a new strategy to image-text matching aware adversarial training. Reed \etal \cite{reed2016learning} propose generative
adversarial what-where network (GAWWN) to enable "where and what" instructions in text-to-image synthesis, which uses extra information to help generate $128{\times}128$ resolution images. StackGAN \etal \cite{han2017stackgan} propose to a two-stage stacking GAN training approach that is able to generate $256{\times}256$ compelling results. Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on targeting descriptions. Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss with a pretrained ImageNet CNN \cite{johnson2016perceptual} and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training.

Learning a continuous mapping from low-dimensional embeddings to complex real data distribution is a long-standing problem. Although GANs have made significant progressive, there are still many  unsolved difficulties, e.g. training instability and high resolution. Wide methods have been proposed to address those tasks, through various stabilization training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, regularization using outside knowledge (e.g. image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}, or multiple discriminators  \cite{metz2016unrolled,durugkar2016generative,yang2017lr}. While note that our method does not use any extra information apart from training paired text and images. Moreover, it is easy to see the training difficulty grows significantly as targeting image resolution increases.

@@

Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks such as image classification \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified,long2015fully}. DSN \cite{lee2015deeply} proposes deep supervision in hierarchical convolutional layers to increase the discriminativeness of feature representations. 
Our method is partially inspired by supervised CNNs with deep supervision \cite{lee2015deeply,xie2015holistically}. Our proposed hierarchically-nested adversarial supervision enhances layer representations to support final high resolution outputs.   
\begin{figure}[t]
	\centering
	%	\includegraphics[width=0.48\textwidth]{}
	\caption{} \label{fig:archs}
\end{figure}

@@

 \begin{algorithm}
 	\caption{Multi scale GAN training algorithm with step size $\alpha$, number of iteration $S$, we omit the batch index and summarize the algorithm using SGD for simplicity.}
 	\label{CHalgorithm}
 	\begin{algorithmic}[1]
 		\For{$i \gets 1 \textrm{ to } S$ }
 		\For{$k \gets 1 \textrm{ to } ncritic$}
 		\State Sample two noise batch $z_1, z_2 \sim p(z)$.
 		\State Sample one batch of matching and mismatching image text pair $\{X, t\}$,  $\{X, \hat{t}\}$.
 		\State Generate fake image samples for both $t$ and $\hat{t}$
 		\begin{equation}
 		\begin{split}
	 		& {o} = G(t, z_1) \\
	 		& {\hat{o}} = G(\hat{t}, z_2) 
 		\end{split}
 		\end{equation}
	 		\For{each discriminator $D_i$ }
		 		\State Update $D_i$ by descending the gradient of loss \ref{equ:totalD}:
		 		\begin{equation}
		 		   	\theta_{D_i} = \theta_{D_i}  - \nabla_{\theta_{D_i}} \mathcal{L}_d(D_i, X_i,o_i,\hat{o_i}, t,\hat{t})
		 		\end{equation}
	 		\EndFor
 		\EndFor
 		\State Update the generator by descending it's stochastic gradient of loss \ref{equ:totalG}:
 		\begin{equation}
 		\theta_{G} = \theta_{G}  - \nabla_{\theta_{G}} \mathcal{L}_g(G, o, \hat{o}, t)
 		\end{equation}

@@

\textbf{Discriminator} The discriminator simply contains consecutive stride-2 conv layers with BN and LeakyReLU (the depth changes according to the input size) until the feature map has $512{\times}4{\times}4$ dimension. There two branches are added on top of it for multi-purpose discriminator design (see next section) . One is a direct $4{\times}4$ conv layers to produce a 2-d vector to classify real and fake. Another one first concatenate $128{\times}4{\times}4$ text embedding (replicated from a $128$-d text embedding). Then we use an $1{\times}1$ conv to fuse text and image information; it is critical to guarantee the semantic consistency in the final results. Finally, a $4{\times}4$ conv layer produces a 2-d vector.

@@

\subsection{Implementation Details}
A algorithm that summarizes the training process of our model is given in Algorithm 1. We train and evaluate our model with a devbox machine. $\alpha$ is set to 0.5, $\beta$ is set to 4. We train our model for 600 epochs for CUB and Oxford, and 120 epochs for COCO dataset. Adam optimizer with momentum 0.5 is used for all experiments.  The initial learning rate is set as 0.0002 and we decrease the learning rate by half every 100 epochs for CUB and Oxford-102 datasets, and 30 for MS COCO.
The number of repeat residual blocks is set to 1 for CUB and Oxford, 2 for COCO. We use batch size 16 for all experiments.

@@

\subsection{Comparative Results}
To validate our method, we compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, TAC-GAN \cite{dash2017tac}, StackGAN \cite{han2017stackgan} and also its improved version StackGAN++ \cite{}, and Progressive GAN \cite{} \footnote{Note that StackGAN++ and Prog.GAN are two very recent released pre-prints we noticed before submission. We acknowledge them as they also target at generating high resolution images, in spite of their differences in motivations and network and training designs from ours. }

@@

Table \ref{table:score} shows the quantitative evaluation. HDGAN achieves significantly improvement compared to other methods. For example, HDGAN improves GAN-INT-CLS by ${\sim}30.1\%$  and ${\sim}8.4\%$ on CUB.

@@

\begin{table}[t] % retrieval
	\begin{center}
		\begin{tabularx}{.268\textwidth}{ccc|c}
			\specialrule{1.5pt}{0pt}{0pt}  
			\multicolumn{3}{c|}{Components}	&  \multirow{2}{*}{Score}	\\ \cline{1-3}
			64	& 128	& 256 			& 		\\ \hline
			&  		&	\checkmark	&	${3.52{\pm}.04}$	\\ 
			&  	\checkmark	&	\checkmark	&		\\
			\checkmark	&  			&	\checkmark	&  ${4.14{\pm}.03}$		\\
			\checkmark	&  \checkmark		&	\checkmark	&	${4.01{\pm}.04}$ \\

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
This paper presents an novel method to deal with the challenging task of generating synthetic photographic image conditioned on semantic image descriptions, which is an effective end-to-end trainable single stream (vanilla-like) network that can generate high resolution images (e.g. $512^2$). Our method leverages the deep representations of convolutional layers and introduces accompanying hierarchical-nested adversarial training to regularize intermediate representations in order to capture the complex image statistics. We present an intuitive as well as extensile network architecture to push generated images to high resolutions as well as preserve semantics and details. 
We apply multi-purpose adversarial learning at multiple nested scales to encourage more effective multimodal (i.e. image and text) information alignment in order to enhance generators to approach real distributions. 
With extensive experimental validation on three major datasets, our method significantly improves previous state of the arts.

@@

%%%%%%%%% BODY TEXT
\section{Introduction}
Generating photographic image conditional on arbitrary semantic description is an important problem in generative model research \cite{reed2016generative}. However, insufficient methods have been successfully developed to address this task due to its particular challenges. Text-to-image synthesis is similar to conventional generative tasks, which aim to translate a low-dimensional embedding  to a much more complex RGB image space.  Differently, the embedding space of the former is induced by semantic descriptions. Therefore, this task requires the generated images to be \textit{semantically consistent}, i.e., the generated images not only preserve sketch concepts of descriptions but also fine-grained descriptive details in image pixels.

Generative adversarial networks (GANs) have become the main solution to this task. 
Reed \etal \cite{reed2016generative} is th first to address this task through a GAN based framework. But this method only handles image up to $64^2$ resolution and can barely generate vivid object details.
Based on this method, Zhang \etal \cite{han2017stackgan} present a successful approach (StackGAN) by stacking another low-to-high resolution GAN to generate high-quality $256^2$ images, with two separate stage training. Later on, Dong \etal \cite{dong2017semantic} propose to bypass the difficult of translate vector embedding to RGB images and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-rendering an arbitrary-style training ($128^2$) image conditioned on a targeting semantic description. But its high resolution synthesis ability is unclear. 
At present, how to train from the low-dimensional text space to synthesize high resolution and diverse images in an end-to-end manner is still an open and attractive question.

We outline several empirical reasons for the challenges of text-to-image synthesis using GANs. The first is the fundamental difficulty of balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}. %How to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients. 
The second is the huge pixel space in high resolution images \cite{han2017stackgan}. 
An effective strategy to regularize generators is critical to help capture the complex image statistics \cite{huang2016stacked} as well as preserve semantic consistency. 
%The first reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. 
% Keeping semantic consistency as well as diversity
%The first reason comes from the fundamental difficulty of balancing the stability between generators and discriminators. There are a rich number of literature trying to stabilize GAN training \cite{salimans2016improved} and regularize networks \cite{huang2016stacked}. 
%But especially for text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important and needs careful consideration. The second reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators to generate effective gradients, as well as generators to prevent gradient vanishing. 
With careful consideration of these outlined problems, in this paper, we propose a novel fully end-to-end method that can directly model high resolution image statistics and generate semantic consistent and photographic image up to $512^2$ resolution. The contributions are described follows.

Our generator is a more like simple vanilla-like GAN, without needing any inside text conditioning \cite{han2017stackgan} or image label supervision \cite{dash2017tac}. To tackle the problem of the big leap from the text space to the high resolution image space, our insight is to leverage hierarchical representations with additional implicit constraints. 
We introduce accompanying hierarchically-nested objective at intermediate layers to play adversarial games to encourage the generator approaching real distribution. 
We also propose a generator network structure design to cooperate our multi-scale nested discriminators more effectively.
To better make use of image and text information in GAN training, 
\textcolor{red}{we enforce nested discriminators at different scales can simultaneously differentiate real and fake, image-text pairs, images, and patches.}
This multi-purpose conditional adversary is mutually beneficial to allow each only focuses on respect duties. 
%It is a regularization to limit the discriminators to use unexpected information to make decision. 
We validate our proposed method on three datasets, i.e. CUB birds \cite{welinder2010caltech}, Oxford-102 flowers \cite{Nilsback08}, and large-scale COCO datasets \cite{lin2014microsoft}. Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts. All source code will be released.

\section{Related Work}
We discussed related methods as well as further clarify the novelty of our method comparing with them.

@@

Text-to-image synthesis not only requires diverse and high-quality generation but also requires precise semantically consistent mapping in the image space.  Reed \etal \cite{reed2016generative} introduce a method that can generate $64^2$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}. This method presents a new strategy to image-text matching aware adversarial training. Reed \etal \cite{reed2016learning} propose generative
adversarial what-where network (GAWWN) to enable "where and what" instructions in text-to-image synthesis, which uses extra information to help generate $128^2$ resolution images. StackGAN \etal \cite{han2017stackgan} propose to a two-stage stacking GAN training approach that is able to generate $256^2$ compelling results. Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on targeting descriptions. Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss with a pretrained ImageNet CNN \cite{johnson2016perceptual} and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training.

Learning a continuous mapping from low-dimensional embeddings to complex real data distribution is a long-standing problem. Although GANs have made significant progressive, there are still many  unsolved difficulties, e.g. training instability and high resolution. Wide methods have been proposed to address those tasks, through various stabilization training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, regularization using outside knowledge (e.g. image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}, or multiple discriminators  \cite{metz2016unrolled,durugkar2016generative,yang2017lr}. While our method does not use any extra information apart from training paired text and images. Moreover, it is easy to see the training difficulty grows significantly as targeting image resolution increases.

@@

Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks such as image classification \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified,long2015fully}. DSN \cite{lee2015deeply} proposes deep supervision in hierarchical convolutional layers to increase the discriminativeness of feature representations. 
Our hierarchically-nested adversarial adversarial objective is partially inspired by supervised CNNs with deep supervision \cite{lee2015deeply,xie2015holistically}. 
%Our proposed hierarchically-nested adversarial supervision enhances layer representations to support final high resolution outputs.   
\begin{figure}[t]
	\centering
	%	\includegraphics[width=0.48\textwidth]{}
	\caption{} \label{fig:archs}
\end{figure}

@@

 \begin{algorithm}
 	\caption{Multi scale GAN training algorithm with step size $\alpha$, number of iteration $S$, we omit the batch index and summarize the algorithm using SGD for simplicity.}
 	\label{CHalgorithm}
 	\begin{algorithmic}[1]
 		\For{$i \gets 1 \textrm{ to } S$ }
 		\For{$k \gets 1 \textrm{ to } ncritic$}
 		\State Sample two noise batch $z_1, z_2 \sim p(z)$.
 		\State Sample one matching image text pair $\{x, t\}$ and mismatched one $\{x, \hat{t}\}$.
 		\State Generate fake image samples for both $t$ and $\hat{t}$
 		\begin{equation}
 		\begin{split}
	 		& {o} = G(t, z_1) \\
	 		& {\hat{o}} = G(\hat{t}, z_2) 
 		\end{split}
 		\end{equation}
	 		\For{each discriminator $D_i$ }
		 		\State Update $D_i$ by descending the gradient of loss \ref{equ:totalD}:
		 		\begin{equation}
		 		   	\theta_{D_i} = \theta_{D_i}  - \nabla_{\theta_{D_i}} \mathcal{L}_d(D_i, X_i,o_i,\hat{o_i}, t,\hat{t})
		 		\end{equation}
	 		\EndFor
 		\EndFor
 		\State Update the generator by descending it's stochastic gradient of loss \ref{equ:totalG}:
 		\begin{equation}
 		\theta_{G} = \theta_{G}  - \nabla_{\theta_{G}} \mathcal{L}_g(G, o, \hat{o}, t)
 		\end{equation}

@@

\textbf{Discriminator} The discriminator simply contains consecutive stride-2 conv layers with BN and LeakyReLU until the feature map has $512{\times}4{\times}4$ dimension. There two branches are added on top of it for multi-purpose discriminator design (see next section) . One is a direct $4{\times}4$ conv layers to produce a 2-d vector to classify real and fake. Another one first concatenate $128{\times}4{\times}4$ text embedding (replicated from a $128$-d text embedding). Then we use an $1{\times}1$ conv to fuse text and image information; it is critical to guarantee the semantic consistency in the final results. Finally, a $4{\times}4$ conv layer produces a 2-d vector.

@@

\subsection{Implementation Details}
A algorithm that summarizes the training process of our model is given in Algorithm 1. We train and evaluate our model with a devbox machine. $\alpha$ is set to 0.5, $\beta$ is set to 4. We decrease the learning rate by half every 100 epochs for CUB and Oxford-102 datasets, and 30 for MS COCO. We train our model for 600 epochs for CUB and Oxford, and 120 epochs for COCO dataset. Adam optimizer is used for all experiments.
The number of repeat residual blocks is set to 1 for CUB and Oxford, 2 for COCO. We use batch size 16 for all experiments.

@@

\subsection{Comparative Results}
To validate our method, we compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, TAC-GAN \cite{dash2017tac}, StackGAN \cite{han2017stackgan} and also its improved version StackGAN++ \cite{}, and Progressive GAN \cite{} \footnote{Note that StackGAN++ and Prog.GAN are two very recently released pre-prints we noticed before submission. We acknowledge them as they also target at generating high resolution images, in spite of their differences in motivations and network and training designs from ours. }

@@

Table \ref{table:score} shows the quantitative evaluation. HDGAN achieves significantly improvement compared to other methods. For example, HDGAN improves GAN-INT-CLS by ${\sim}30.1\%$  and ${\sim}8.4\%$ on CUB. It also significantly outperforms StackGAN StackGAN++.
HDGAN achieves competitive results with TAC-GAN on the Oxford flower dataset. TAC-GAN uses image labels to increase the discriminability of generators, while we do not use any extra knowledge.

@@
